### 2019-10-21 ch6_bred/content.tex
~

One of the central cellular processes underlying development is transcriptional regulation. 
Changes in transcription factor activity induce chromatin modifications, 
chromatin remodelling, a differential recruitment of the basal transcriptional machinery\cite{coulon_eukaryotictranscriptionaldynamics_2013}.
Modelling the dynamics of gene regulation is therefore essential to better understand
why a cellular dynamic processes progresses through several steps,
and what goes wrong in the case of disease.

The dynamics of gene regulation has classically been studied using time series data \cite{bar-joseph_studyingmodellingdynamic_2012}. When dynamic processes progress asynchronously, such as in hematopoiesis, time series data are usually obtained by sorting different transition states and assessing bulk gene expression and transcription factor binding within the population \cite{novershtern_denselyinterconnectedtranscriptional_2011, may_dynamicanalysisgene_2013, jojic_identificationtranscriptionalregulators_2013, goode_dynamicgeneregulatory_2016}. Alternatively, time series data can also be generated by synchronizing the dynamic process between cells. However, issues with time-resolution, heterogeneity and good in vivo synchronization models can often limit the predictive power of the dynamic models of gene regulation which can be constructed \cite{bar-joseph_studyingmodellingdynamic_2012}.

One of the main advantages of single-cell transcriptomics is the ability to quantify the exact cellular state of thousands of cells per experiment. The intercellular heterogeneity caused by naturally occurring biological stochasticity \cite{padovan-merhar_usingvariabilitygene_2013} can be exploited to predict regulatory interactions between transcription factors (TFs) and their target genes. The computational tools that infer gene regulatory networks (GRNs) from omics datasets are called network inference (NI) methods.
% TODO: talk about bulk NI

@@

In order to compute a case-wise GRN for a single sample, Kuijjer et al. \cite{kuijjer_estimatingsamplespecificregulatory_2019} and Liu et al. \cite{liu_personalizedcharacterizationdiseases_2016} employ similar strategies, namely by computing the difference of computing a static GRN for all the cases, and computing a static GRN for all the cases minus one. Since this procedure needs to be repeated for every case in the dataset, and because NI methods are already amongst the most computationally intensive analyses to perform on omics data, this methodology is not applicable for large omics datasets.
Another case-wise NI method, SCENIC \cite{aibar_scenicsinglecellregulatory_2017} infers case-wise GRNs by first inferring a static GRN using GENIE3 \cite{huynh-thu_inferringregulatorynetworks_2010}. GENIE3 is a static NI method which uses Random Forests \cite{breiman_randomforests_2001} feature importance scores to prioritise candidate regulators for a particular target gene. SCENIC then post-processes the static GRN to determine whether an interaction is enriched for particular cases, resulting in a case-wise GRN. 
In short, while several case-wise NI methods thus already exist, their implementation consisted of post-processing a static GRN to arrive at a case-wise GRN.

In this work, we introduce \texttt{bred}, the first 'true' case-wise NI method. For each interaction in the inferred case-wise GRN, \texttt{bred} predicts both the regulatory strength and its effect. 
The case-wise GRNs -- or 'case-wise regulomes' -- can be analysed analogously to transcriptomics data; for example by clustering samples, inferring trajectories, or finding differentially activated regions.
We demonstrate \texttt{bred} by applying it to a single-cell dataset of 22'122 hematopoietic cells from the Tabula Muris project \cite{schaum_singlecelltranscriptomics20_2018}, and to a collection of 14'963 bulk omics samples from The Cancer Genome Atlas project \cite{weinstein_cancergenomeatlas_2013}.

\section{Results}

\subsection{Hematopoietic cells from Tabula Muris}
From the Tabula Muris \cite{schaum_singlecelltranscriptomics20_2018} project, we selected all cells involved in some part of the hematopoietic lineage tree. We computed case-wise GRNs between 22'122 remaining single cells, for the 2000 most variable target genes and a subset of transcription factors as regulators.

To summarise the similarity in GRNs across cases, we first visualise a dimensionality reduction of the case-wise GRNs, where every dot represents a single GRN (Figure~\ref{fig:tabmur}A). The dimensionality reduction was computed by applying Fruchterman-Reingold \cite{fruchterman_graphdrawingforcedirected_1991} on the $k$-nearest-neighbour ($k$NN) graph of the case-wise GRN vectors. On the same $k$NN graph, the cells were clustered using the Louvain \cite{blondel_fastunfoldingcommunities_2008} clustering algorithm, and the clusters were labelled using prior information from Tabula Muris.
For each cluster, we retained the 50 interactions with the highest mean importance scores (Figure~\ref{fig:tabmur}B). In the visualisation, each node represents a gene, each edge an interaction, and the colour represents which cluster this interaction belongs to.

For the most part, clusters that are proximate in the dimensionality reduction (Figure~\ref{fig:tabmur}A) are also closely connected in the GRN network view (Figure~\ref{fig:tabmur}B). Notably, interactions from the different B cell clusters are almost not connected amongst each-other, while in the dimensionality reduction they re very proximate. Retaining more edges could result in the different B cells being connected in the GRN network view.

At the centre of the network lie many strongly connected interactions which are not specific for any particular cluster, but instead are common to almost all of the clusters. These are likely housekeeping genes or genes involved in key hematopoietic processes.

\begin{figure}[htb!]
	{\raggedright\textbf{A}}
	\begin{center}\includegraphics[width=\linewidth]{fig/tabula_muris_hema/plot_fr_cropped.png}\end{center}
	{\raggedright\textbf{B}}
	\begin{center}\includegraphics[width=.9\linewidth]{fig/tabula_muris_hema/grouped_interactions.pdf}\end{center}
	\caption{
		\textbf{22'122 case-wise GRNs of hematopoietic cells from the Tabula Muris project.}
		\textbf{A:} Each dot in this dimensionality reduction corresponds to the GRN of a single cell. The dimensionality of the cell-specific regulome matix was reduced using Fruchterman-Reingold and were clustered using Louvain clsutering, after which the clusters were relabelled using the meta information from Tabula Muris.
		\textbf{B:} Per cluster, the 50 interactions with the highest mean importance score are visualised.
	}
	\label{fig:tabmur}
\end{figure}

\subsection{The Cancer Genome Atlas}
We included all available RNA-seq profiles from The Cancer Genome Atlas. In total, we computed case-wise GRNs for 14'963 tumour samples from 50 sub-projects, including 44 different cancer entities. Clusters of case-wise GRNs were relabelled by the project they originate from, or by the cell types or organs the samples originate from.

Most groups of interactions are highly specific to just one cancer type. Samples from the CPTAC project were split into two groups, clustering together with LUAD (lung adenocarcinoma) and kidney carcinoma samples. According to the meta-information of CPTAC profiles, these samples consist of lung, kidney, and uterus adenocarcinomas, explaining the split in CPTAC samples.

%TODO: Extend !!

\begin{figure}[htb!]
	{\raggedright\textbf{A}}
	\begin{center}\includegraphics[width=.8\linewidth]{fig/tcga/plot_fr_cropped.png}\end{center}
	{\raggedright\textbf{B}}
	\begin{center}\includegraphics[width=.85\linewidth]{fig/tcga/grouped_interactions_2.pdf}\end{center}
	\caption{
		\textbf{14'963 case-wise GRNs of cancer bulk profiles from The Cancer Genome Atlas project.}
		\textbf{A:} The different profiles are visualised and clustered according to their regulomic similarities.
		\textbf{B:} Visualisation of the strongest interactions per cluster shows both pathways distinct to particular cancer entities as well as pathways common to multiple cancer entities.
	}
	\label{fig:tcga}
\end{figure}

@@

The \texttt{bred} algorithm is a novel approach for directly computing case-wise GRNs for single-cell omics and bulk omics profiles alike. We applied the method to 22'122 hematopoietic cells and 14'963 cancer profiles, showing that interactions are often grouped together in modules specific for certain cell types, tissue types, or cancer types.

In this work, we only applied clustering methods to the case-specific 'regulome profiles', but other types of computational methods can be used to annotate and explore case-specific GRNs, such as trajectory inference and differential expression.

Going forward, we will provide further functional validation of the results generated by \texttt{bred}, as well as benchmark the algorithm against various real and \textit{in silico} datasets.

@@

\subsection{Inferring case-wise GRNs}
The task of inferring a static GRN (Figure~\ref{fig:simplify}A) can be reduced to a simpler problem, namely: for every target $T$, predict which of the potential regulators $R_i$ regulate $T$ (Figure~\ref{fig:simplify}B). This simplification allowed GENIE3 \cite{huynh-thu_inferringregulatorynetworks_2010} to use Random Forest's \cite{breiman_randomforests_2001} feature importance scores for inferring GRNs. Namely, a Random Forest is trained to predict the expression of a target gene of interest from the expression of potential regulators. The resulting Random Forest inherently allows to extract a feature importance score by observing the effect of each regulator in making a good prediction for the target expression. As in GENIE3, the target expression is first scaled to normalise feature importance scores across different targets.

@@

@@

>>>>

One of the central cellular processes underlying development is transcriptional regulation. 
Modelling the dynamics of gene regulation is therefore essential to better understand
why a cellular dynamic processes progresses through several steps,
and what goes wrong in the case of disease. 
Regulatory dynamics is classically studied using time series data \cite{bar-joseph_studyingmodellingdynamic_2012}. When dynamic processes progress asynchronously, such as in hematopoiesis, time series data are usually obtained by sorting different transition states and assessing bulk gene expression and transcription factor binding within the population \cite{novershtern_denselyinterconnectedtranscriptional_2011, may_dynamicanalysisgene_2013, jojic_identificationtranscriptionalregulators_2013, goode_dynamicgeneregulatory_2016}. Alternatively, time series data can also be generated by synchronising the dynamic process between cells. However, issues with time-resolution, heterogeneity and good \textit{in vivo} synchronisation models can often limit the predictive power of the dynamic models of gene regulation which can be constructed \cite{bar-joseph_studyingmodellingdynamic_2012}.

Network inference (NI) methods are computational tools which use large omics datasets to predict which genes are regulated by which transcription factors. While accuracy of the network of predicted regulatory interactions is lower in comparison to experimental validation techniques, NI methods offer an unbiased and high-throughput insight into the regulatory dynamics of a biological system.
The output of a network inference is thus a graph, where nodes represent genes and edges denote a regulatory interaction between a regulator and a target gene. Interactions have two properties: its regulatory strength (a positive real value) and its effect (promoting or repressing).

@@

In order to compute a case-wise GRN for a single sample, Kuijjer et al. \cite{kuijjer_estimatingsamplespecificregulatory_2019} and Liu et al. \cite{liu_personalizedcharacterizationdiseases_2016} employ similar strategies, namely by computing the difference of computing a static GRN for all the cases, and computing a static GRN for all the cases minus one. Since this procedure needs to be repeated for every case in the dataset, and because NI methods are already amongst the most computationally intensive analyses to perform on omics data, this methodology is not applicable for large omics datasets.
Another case-wise NI method, SCENIC \cite{aibar_scenicsinglecellregulatory_2017} infers case-wise GRNs by first inferring a static GRN using GENIE3 \cite{huynh-thu_inferringregulatorynetworks_2010}. GENIE3 is a static NI method which uses Random Forests (RFs) \cite{breiman_randomforests_2001} variable importance scores to prioritise candidate regulators for a particular target gene. SCENIC then post-processes the static GRN to determine whether an interaction is enriched for particular cases, resulting in a case-wise GRN.

Thus, while several case-wise NI methods have already been proposed, their implementation consisted of post-processing a static GRN to arrive at a case-wise GRN. As such, these methods will most likely recover the interactions that are prevalent in the whole population, and will miss interactions that are specific to only a sub-population.

In this work, we introduce \texttt{bred}, the first 'true' case-wise NI method. It uses a modified version of the RF variable importance scores used by GENIE3 and SCENIC to compute importance values for each profile and each interaction separately, as well as predict the effect of each interaction (activating or repressing). We generate case-wise GRNs -- or case-wise regulomes -- for 14'963 profiles from The Cancer Genome Atlas (TCGA) \cite{weinstein_cancergenomeatlas_2013}, resulting in 6'464'915 predicted case-wise interactions.
We analyse these case-wise regulomes by clustering them and detecting highly activated interactions.

\section{Results}
At the time of writing, the TCGA database contains 14'963 profiles from 44 different cancer entities. We used the \texttt{bred} algorithm to infer case-wise regulomes for each of these profiles. In total, we detected 73'140 unique interactions and, on average, 7'231 active interactions per profile. Dimensionality reduction and clustering of the case-wise regulome data provides a visual overview of the different subpopulations (Figure~\ref{fig:tcga_dimred}).

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.6\linewidth]{fig/tcga/plot_fr_cropped.png}
	\caption{
		\textbf{Visualisation of 14'963 case-wise regulomes of cancer profiles from The Cancer Genome Atlas project.} 
		Dimensionality reduction of the case-wise regulomes was performed by applying Fruchterman-Reingold \cite{fruchterman_graphdrawingforcedirected_1991} on the $k$-nearest-neighbour graph ($k=100$) of highly similar regulomes (Spearman correlation). The samples were clustered with Louvain clustering \cite{blondel_fastunfoldingcommunities_2008} and each cluster was assigned an ontology term from the NCI thesaurus ontology \cite{sioutos_ncithesaurussemantic_2007} which best fits the sample in the cluster. Clusters for which the term has a positive predictive value (PPV) lower than 0.5 are marked with an asterisk (*). More detailed information on the enrichment of particular terms or metadata for each of the clusters can be found in Figures~\ref{fig:cluslab1}--\ref{fig:cluslab7}.
	}
	\label{fig:tcga_dimred}
\end{figure}

For each cluster, we computed the average importance of each interaction. Retaining the 100 strongest interactions (Figure~\ref{fig:tcga_network}) shows that different cancer entities have vastly different regulomes, yet often have shared regulators and interactions (Table~\ref{tab:oncogenes}).

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.85\linewidth]{fig/tcga/grouped_interactions.pdf}
	\caption{
		\textbf{Visualisation of the strongest interactions per cluster} shows both pathways distinct to particular cancer entities as well as pathways common to multiple cancer entities.
	}
	\label{fig:tcga_network}
\end{figure}

Performing a more in-depth analysis of particular clusters can reveal distinct sub-populations within. For example, when comparing samples of normal and healthy tissue within breast carcinoma (Figure~\ref{fig:zoom17}), a significant number if interactions are predicted to have been turned off (top), while others have been turned on (middle, bottom). Similar observations can be made for other clusters, such as for melanocytic neoplasm (Figure~\ref{fig:zoom9}) and kidney carcinoma (Figure~\ref{fig:zoom12}).

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.7\linewidth]{fig/tcga/zoom_cluster17_brca_plot.pdf}
	\includegraphics[width=.7\linewidth]{fig/tcga/zoom_cluster17_brca_heatmap.pdf}
	\caption{
		\textbf{In-depth view of cluster 17, breast carcinoma.} 
		\textbf{Top:} A dimensionality reduction of the samples, coloured according to multiple sources of meta-data. 
		\textbf{Bottom:} The samples were ordered linearly with SCORPIUS (see trajectory in \textbf{Top}) in order to visualise regulome activity in the form of a heatmap.
	}
	\label{fig:zoom17}
\end{figure}

@@

The \texttt{bred} algorithm is a novel approach for directly computing case-wise regulomes for single-cell omics and bulk omics profiles alike. We used \texttt{bred} to infer case-wise regulomes for 14'963 cancer profiles from The Cancer Genome Atlas project. Analysing the results using common omics algorithms (dimensionality reduction, clustering, enrichment) has shown that regulatory interactions are often specific to particular cancer types, but can also be shared between several cancer types. Ultimately, this analysis has resulted in a list of candidate oncogenic genes and interactions per cancer type, though further analysis and validation is required to confirm their oncogenicity.

Future perspectives include applying it on single-cell omics data (e.g. from Tabula Muris \cite{schaum_singlecelltranscriptomics20_2018}) and benchmarking the algorithm against \textit{in silico} datasets (e.g. produced by \texttt{dyngen} \cite{cannoodt_dyngenbenchmarkingsilico_2019}).

@@

\subsection{Inferring case-wise regulomes}
The task of inferring a static GRN (Figure~\ref{fig:simplify}A) can be reduced to a simpler problem, namely: for every target $T$, predict which of the potential regulators $R_i$ regulate $T$ (Figure~\ref{fig:simplify}B). This simplification allowed GENIE3 \cite{huynh-thu_inferringregulatorynetworks_2010} to use Random Forest's \cite{breiman_randomforests_2001} feature importance scores for inferring GRNs. Namely, a Random Forest is trained to predict the expression of a target gene of interest from the expression of potential regulators. The resulting Random Forest inherently allows to extract a feature importance score by observing the effect of each regulator in making a good prediction for the target expression. As in GENIE3, the target expression is first scaled to normalise feature importance scores across different targets.

@@

% TODO: describe cluster relabelling, see figures fig:cluslab

@@

\section{Supplementary information}

\begin{table}[H]
	\scriptsize
	\caption{\textbf{Prioritisation of genes, ranked according to page-rank value.} The majority of these genes are already known to be involved in oncogenesis (data not shown).} \label{tab:oncogenes}
	\begin{tabularx}{\linewidth}{XX}
		\hline
		Cluster name & Top 4 genes, page rank \\
		\hline\hline
		Acute Leukemia & HSPA1A, HSPA1B, HOXA10, HOXA9 \\
		ALL & DDX3Y, XIST, RN7SL128P, TXLNGY \\
		BL & KIAA0226L, XIST, TCL1A, NUGGC \\
		BRCA & LINC00993, IRX5, ATP8A2P1, ENSG00000234918 \\
		Connective and Soft Tissue Disorder * & HOXA11, HOXC9, HOXA10, HOXC10 \\
		CPTAC \#1 & SLC22A2, CUBN, XIST, UMOD \\
		CPTAC \#2 & RN7SL752P, SCARNA13, XIST, RNY1 \\
		Diffuse Large B-Cell Lymphoma & PLA2G2D, ENSG00000224137, CCL25, MS4A1 \\
		Digestive System Disorder & MEP1A, LGALS4, MUC13, CDX1 \\
		Glioma & NCAN, GPM6A, MBP, OLIG2 \\
		Kidney Carcinoma & ACSM2A, SLC22A2, NAT8, UMOD \\
		LIHC & AGXT, ITIH3, ITIH1, HRG \\
		LUAD & SFTPA2, SFTPD, NAPSA, SFTA2 \\
		Melanocytic Neoplasm & MLANA, RPS4Y1, PMEL, TYR \\
		MM & CD96, GPRC5D, FGFR3, IGLV1-41 \\
		Peripheral Nervous System Disorder & TH, DBH, PENK, HAND2 \\
		PRAD & TRGC1, NKX3-1, ACPP, RPL7P16 \\
		Squamous Cell Carcinoma & TP63, SPRR2F, RPS4Y1, CDKN2B \\
		THCA & ENSG00000240237, TG, TPO, RPS4Y1 \\
		Transitional Cell Carcinoma & DHRS2, UPK2, PADI3, VGLL1 \\
		UCEC & DLX5, MSX1, HOXB5, HOXB8 \\
		\hline
		\	\end{tabularx}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=.95\linewidth,page=1]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=2]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=3]{fig/tcga/cluster_labelling.pdf}
	\caption{
		\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 1--3.} Cluster 2 is mainly made up of disorders in female reproductive organs, and should have been labelled as such.
	}
	\label{fig:cluslab1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=.95\linewidth,page=4]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=5]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=6]{fig/tcga/cluster_labelling.pdf}
	\caption{
		\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 4--6.} Cluster 5 is mainly made up of renal cell carcinoma, and should have been labelled as such. Cluster 6 is aptly named, but mainly consists of neuroblastoma (NB), pheochromocytoma (PC), and paraganglioma (PG) disorders.
	}
	\label{fig:cluslab2}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=.95\linewidth,page=7]{fig/tcga/cluster_labelling.pdf}
\includegraphics[width=.95\linewidth,page=8]{fig/tcga/cluster_labelling.pdf}
\includegraphics[width=.95\linewidth,page=9]{fig/tcga/cluster_labelling.pdf}
\caption{
	\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 7--9.} 
}
\label{fig:cluslab3}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=.95\linewidth,page=10]{fig/tcga/cluster_labelling.pdf}
\includegraphics[width=.95\linewidth,page=11]{fig/tcga/cluster_labelling.pdf}
\includegraphics[width=.95\linewidth,page=12]{fig/tcga/cluster_labelling.pdf}
\caption{
	\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 10--12.} 
	Cluster 11 contains mostly Lung Adenocarcinoma (LUAD), but also Lung Squamous Cell Carcinoma (LUSC), and thus should have been labelled Lung Carcinoma instead.
}
\label{fig:cluslab4}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=.95\linewidth,page=13]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=14]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=15]{fig/tcga/cluster_labelling.pdf}
	\caption{
		\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 13--15.} 
		Cluster 13 contains a mixture of cancer types, and should have been labelled 'Mixed'.
	}
	\label{fig:cluslab5}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=.95\linewidth,page=16]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=17]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=18]{fig/tcga/cluster_labelling.pdf}
	\caption{
		\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 16--18.} 
	}
	\label{fig:cluslab6}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=.95\linewidth,page=19]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=20]{fig/tcga/cluster_labelling.pdf}
	\includegraphics[width=.95\linewidth,page=21]{fig/tcga/cluster_labelling.pdf}
	\caption{
		\textbf{Prioritisation of NCI terms and other forms of meta-data used to annotate clusters 19--21.} 
		Cluster 21 contains a mixture of cancer types, mostly lung carcinoma and endometrial carcinoma.
	}
	\label{fig:cluslab7}
\end{figure}

\subsection{Melanocytic neoplasm}

\begin{figure}[H]
	A
	\begin{center}\includegraphics[width=.85\linewidth]{fig/tcga/zoom_cluster9_melanocytic-neoplasm_plot.pdf}\end{center}
	B
	\begin{center}\includegraphics[width=.85\linewidth]{fig/tcga/zoom_cluster9_melanocytic-neoplasm_heatmap.pdf}\end{center}
	\caption{
		\textbf{In-depth view of cluster 9, melanocytic neoplasm.} 
		\textbf{A:} A dimensionality reduction of the samples, coloured according to multiple sources of meta-data. 
		\textbf{B:} The samples were ordered linearly with SCORPIUS (see trajectory in \textbf{A}) in order to visualise regulome activity in the form of a heatmap.
	}
	\label{fig:zoom9}
\end{figure}

\subsection{Kidney carcinoma}

\begin{figure}[H]
	A
	\begin{center}\includegraphics[width=.85\linewidth]{fig/tcga/zoom_cluster12_kidney-carcinoma_plot.pdf}\end{center}
	B
	\begin{center}\includegraphics[width=.85\linewidth]{fig/tcga/zoom_cluster12_kidney-carcinoma_heatmap.pdf}\end{center}
	\caption{
		\textbf{In-depth view of cluster 12, kidney carcinoma.} 
		\textbf{A:} A dimensionality reduction of the samples, coloured according to multiple sources of meta-data. 
		\textbf{B:} The samples were ordered linearly with SCORPIUS (see trajectory in \textbf{A}) in order to visualise regulome activity in the form of a heatmap.
	}
	\label{fig:zoom12}
\end{figure}
